Trends of SDR in Thessaloniki

### 2023-06-29 Article.Rmd
Commit 2023-06-29 11:17
Commit 2023-06-29 12:17

@@

Multiple studies attempt to evaluate the phenomenon and the potential causes [@Ohvril2009; @Schwarz2020; @Wild2009; @Wild2012; @Xia2007; @Zerefos2009; and references therein].
<!-- causes say less we don't do that -->

There is a also a need to evalutate the trends on different location

>>>>

The interaction between Aerosols and clouds, among other factors, has been analysed with modeling [@Li2016; @Samset2018], showing the existence of feedback mechanisms between the two.

Similar links have been showed with observational data [@Ohvril2009; @Schwarz2020; ]

@@

Multiple studies attempt to evaluate the phenomenon and the potential causes [;  @Wild2012; @Xia2007; @Zerefos2009; and references therein].
<!-- causes say less we don't do that -->

Investigate multiple interaction @Li2016 @Samset2018 data analysis and modeling

There is a also a need to evaluate the trends on different location
